\section{Experience}

\cventry{2012--2013}{Lab Assistant}{Institute of Acoustics, Chinese Academy of Sciences}{\textsc{Beijing}}{Key Laboratory of Noise and Vibration Research}{Supervised by Prof. Ming Bao, baoming@mail.ioa.ac.cn}{Established Auditory Localization Lab, mainly responsible for psychophysical settings and ordering required hardware. Specifically, provided desired engineering parameters for the framework, speakers, chips etc.; ordered high frequency professional monitor, laser pointer, LEDs, high precision potentiometer etc.}

\cventry{May, 2013}{Abstract and poster for the meeting}{Annual Meeting --- Vision Science Society 2013}{\textsc{Naples, Florida}}{}{Supervised by Prof. Lihan Chen, clh20000@gmail.com}{Tactile inputs resolve the ambiguous perception of biological point light walkers.}
\begin{itemize}
  \item Abstract -- \textit{Journal of Vision} July 24, 2013 vol. 13 no. 9 article 190.
  \item Poster -- 23.427, Orchid Ballroom, Session: Motion: Biological motion.
\end{itemize}

\cventry{July, 2013}{Abstract for poster presentation}{The 9th Asia-Pacific Conference on Vision (APCV 2013)}{\textsc{Suzhou, Jiangsu}}{}{Supervised by Prof. Lihan Chen, clh20000@gmail.com}{Tactile temporal groupings bias perception of ambiguous point light walkers.}
\begin{itemize}
  \item Poster -- 23.427, Bai Yun Hall, Session: Perceptual grouping, Visual search.
\end{itemize}

\cventry{Aug, 2013}{The Secretary-General}{The 23th World Philosophy Congress}{\textsc{Athens, Greece}}{Delegation of Peking University for 23th WCP}{Supervised by Prof. Jixing Li, pinghenglun@sohu.com}{Responsible for visa application, scheduling, communication with Hellenic Committee, paper submission, publicity, socializing with related participants and security management.}

\cventry{Oct, 2012}{Translator}{International Congress for Traditional Chinese Medicine}{\textsc{Xinmi, Henan}}{Oral translation from English to Chinese during speech}{Supervised by Prof. Mark Harrison, mark.harrison@wuhmo.ox.ac.uk}

\cventry{2013-2014}{Secretary}{China Center for Balance Theory Research, Peking University}{\textsc{Beijing}}{}{Supervised by Prof. Jixing Li, pinghenglun@sohu.com}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

